---
title: "tidymodels with Doctor Who data (2021-48)"
output: html_notebook
---

This is me following the Julia Silge's screencast predicting viewership for Doctor Who episodes

https://juliasilge.com/blog/doctor-who/
https://www.youtube.com/watch?v=T8SSxIo-9Rg 

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
```

## Explore the data

```{r import-data}
episodes <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-11-23/episodes.csv") %>%
  filter(!is.na(uk_viewers))
```
Visualizing raw data (viewership)
```{r exploratory-plot}
episodes %>% 
  ggplot(aes(first_aired, uk_viewers)) +
  geom_line(alpha = 0.8, size = 1.2, color = "midnightblue") +
  labs(x = NULL)
```

There are spikes in christmas specials, season finales, and specials episodes.

## Create a workflow

```{r}
set.seed(1989)

# Building bootstraped resamples with stratification
folds <- bootstraps(episodes,
                    times = 100,
                    strata = uk_viewers)
folds
```

Feature engineering:
We want to build features from the date variable.



```{r}
who_recipe <- 
recipe(uk_viewers ~ first_aired, data = episodes) %>%
  #Function `step_date()` by default creates features for year, month and day of the week.
  # In this case, we're going to just creat a 'year' feature because the data is so small.
  step_date(first_aired, features = "year") %>%
  # `keep_original_cols` argument allows us to decide whether to keep the original date column.
  step_holiday(first_aired,
               holidays = c("NewYearsDay", "ChristmasDay"),
               keep_original_cols = FALSE)

who_recipe
```
Training the recipe (this is not needed, it's just for preview)
```{r}
prep(who_recipe)
```
Checking how the data will look like:
```{r}
prep(who_recipe) %>% bake(new_data = NULL)
```

Now let's make a workflow:
It's useful because it allows to have our pre-processing and modeling in one object, and also because it promotes good statistical practices and helps us avoid common pitfalls.
```{r}
who_wf <- workflow(who_recipe,
                   linear_reg()) 
who_wf
```

## Extract from resampled workflows

By default models are thrown away (it asumes that all you care about is performance). But you can modify that behaviour with the following code:
```{r}
# extract allows to retain stuff objects from the model fit
# extract_fit_engine will extract the trained lm object
# we could also use custom functions!
ctrl_extract <- control_resamples(extract = extract_fit_engine)
```


The previous configuration will generate a new column named 'extracts'
```{r}
doParallel::registerDoParallel()
set.seed(1989)
who_rs <- fit_resamples(who_wf, folds, control = ctrl_extract)
who_rs
```

```{r}
results <- 
  who_rs %>% 
  select(id, .extracts) %>% 
  unnest(.extracts) %>% 
  mutate(coefs = map(.extracts, tidy)) %>% 
  unnest(coefs) %>% 
# For each of the bootstrap resamples we now have the terms and the coefficients!
  filter(term != "(Intercept)")

results
```
If we wanted, we could do a lot of analysis on these bootstraped coefficients!

```{r}
results %>% 
  ggplot(aes(estimate, fill = term)) +
  geom_histogram(alpha = 0.8, bins = 12, show.legend = FALSE) +
  facet_wrap(vars(term), scales = "free")
```

Christimas and New Year episodes have higher viewership, and there is a downward trend over the years.
